Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-07 ms.tex
conclusions 7

In Appendix \ref{app:windheat} we calculate the wind heating rate from
stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter,
$\eta$ (eq.~[\ref{eq:q}]), as a function of age, $\tau_{\star}$, of a
stellar population which is formed impulsively (Fig.~\ref{fig:vwImp}).  
At the earliest times ($\tau_{\star} \lesssim 10^{7}$ yr), the wind
heating rate exceeds 1000 km s$^{-1}$, while much later ($\tau_{\star}
\sim t_{\rm h}$) stellar wind heating dominated by main sequence winds
is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  As shown below in $\S\ref{sec:combined}$ that for the case of quasi-continuous star
formation representative of the average star formation history of loss
mass galaxies, the stellar wind heating rate produced by stellar winds
can also be significant, $v_{\rm w}^{\star} \sim 1000$ km s$^{-1}$.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
  to the total heating rate of the CNM, $\vwO$ ({\it black}),
  including stellar wind heating ({\it orange}), Ia supernovae ({\it
    green}), millisecond pulsars ({\it blue}), and compton heating
  ({\it pink}).  Each heating source varies with black hole mass
  $\Mbh$ calculated for average star formation histories from
  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for
  details).  {\it Middle Panel:} The ratio of the total heating rate
  ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the
  radiating cooling rate ($|\dot{q}_{\rm rad}|$) at the stagnation
  radius. {\it Bottom panel} Parameter $\eta$ characterizing stellar
  mass loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
  $\Mbh$, calculated for average star formation histories from and the
  ratio of Ia radius to stagnation radius as a function of $\Mbh$.}
  %The Ia radius calculated from equation~\eqref{eq:rIa} based on
  %convolving the average star formation histories with the SN Ia DTD.
  %The stagnation radius is calculated from \eqref{eq:stag_simple}
  %using the total heating rate for each $\Mbh$ shown in the top panel
  %assuming a cusp galaxy ($\Gamma=0.8$).}
\end{figure}

@@

If the nuclei of elliptical galaxies are heated in a way similar to
that due to the average star formation history of galaxies with
similar mass, then to first order we predict that $\langle
L_{X}/L_{\rm edd}\rangle$ should be relatively independent of BH mass.
To within the uncertainties, this result is consistent with the
observed down-sizing trend that the average Eddington ratio is seen to
decrease (albeit weakly) with $M_{\bullet}$, although tension is
somewhat greater in the $\epsilon_X= (\epsilon_{\rm
  bol}/0.1)(\Mdot/\MdotEdd)$ model.

%However, one must keep in mind the enormous uncertainty in calculating the
%luminosity of the accretion flow close to the black hole in a single
%waveband based on the feeding rate on larger scales.  If disk outflows carry away most of the infalling mass before it reaches X-ray producing radii (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), then the
%angular momentum of the infalling gas might also influence the X-ray luminosity, in a way
%that could depend systematically on the stellar population and hence $M_{\bullet}$.

@@

Figure \ref{fig:bh_growth} (top panel) also shows that $\dot{M}_{\rm
  C} > \dot{M}_{\rm TI}$ across all black hole masses.  Thus, even if
Compton heating could act to self-stabilize the flow (which, as already
mentioned, appears unlikely), its magnitude appears to be insufficient to
produce a thermally stable accretion rate even given conditions
corresponding to the average star formation history.

@@

\subsection{Local Growth Time of SMBHs }
\label{sec:growth}

@@

The bottom panel of Figure~\ref{fig:bh_growth} shows the SMBH growth
time, $t_{\rm grow} \equiv M_{\bullet}/\dot{M}$, for each accretion rate
shown in the top panel.  For SMBHs which accrete steadily at the rate set by the
stellar wind heating due to the average star formation
history of their host galaxies, we see that $t_{\rm grow}$ exceeds the
Hubble time by 2$-$3 orders of magnitude across all $M_{\bullet}$.
Steady accretion therefore cannot explain the growth of low mass black
holes, a fact which is not surprising given that approximately half of
this growth occurs in AGN radiating within 10 per cent of their
Eddington rate (\citealt{Heckman+04}).  Such high accretion rates
likely instead require an source of gas external to the nuclear
region, triggered either by galaxy mergers associated with the
hierarchical growth of structure or thermal instabilities on larger,
galactic scales (e.g.~\citealt{Ciotti+10}).  In support of this,
\citet{Kauffmann&Heckman09} find that the growth of low mass black
holes is dominated by young stellar bulges which have a log normal
distribution of Eddington ratios peaked at $\Mdot/\dot{M}_{\rm edd} \sim
0.01$. That this distribution is insensitive to galaxy properties
suggests that it is set by SMBH feedback instead of the nuclear gas
supply.

@@

\citet{BergerZauderer+:2012a} infer a flattening of the gas density
profile of the host of J1644+57 on radial scales $r \gtrsim 0.4$ pc (their Fig.~6) which looks
qualitatively similar to the shape density profile we predict for core
galaxies (Fig.~\ref{fig:profiles}, solid line).  To obtain such a flattening on the inferred radial scales would require a black hole of $\Mbh\sim 10^7 \Msun$.  However,  this is inconsistent with the break in the gas density seen at $\sim 0.6$ pc by \citet{BergerZauderer+:2012a}, which should correspond to the break radius of the {\it stellar density} profile, thus implying an unrealistically small SMBH mass of $\Mbh\simeq 100\Msun$ according to the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}.  Alternatively, the observed density break in J1644+57 could result from the outer edge of a sub-parsec nuclear star cluster (e.g., \citealt{Carson+15}).  The high stellar densities of such a compact star cluster could greatly enhance the TDE rate (e.g.~\citealt{Stone&Metzger15}), possibly making this association uncoincidental.

@@

We have calculated steady-state models for the hot gaseous circumnuclear media of quiescent galaxies, under the assumption that gas is supplied exclusively by stellar wind mass loss and heated by shocked stellar winds, supernovae and black hole feedback.  We compute solutions for a range of different black hole masses, heating rates, and observationally-motivated stellar density profiles.  Our numerical results (Table \ref{table:models}) are used to verify and calibrate analytic relationships (Appendix \ref{app:rs}, \ref{app:be}).  The latter are in turn used to explore systematically how the SMBH accretion rate varies with black hole mass and the galaxy's star formation history.  Our results for $\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray luminosities of quiescent SMBHs and low luminosity AGN, and used to address other key questions, such as the thermal stability of their accretion flows.  Our conclusions are summarized as follows.

  \begin{enumerate}
  \item A stagnation radius, $\rs$, divides the nuclear gas between an accretion flow and an
    outward wind. In steady-state the gas inflow rate towards the black hole is proportional to the
    stellar mass enclosed inside of $\rs$.  In the limit of strong heating, the stagnation radius resides interior to the SMBH influence radius and coincides with the Bondi radius (eq.~[\ref{eq:rbondi}]).  In the limit of weak heating ($\zeta < \zeta_c$; eq.~[\ref{eq:zetac}]), the stagnation radius moves to large radii, near or exceeding the stellar break radius $r_b \gg r_{\rm inf}$.

\item The inclusion of thermal conduction results in only moderate changes to the key properties of the flow (e.g. stagnation radius, mass accretion rate, and thermal stability) for causal values of the saturation parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).

\item Radiative cooling has a more pronounced influence on the structure of the gas flow.  The approximate condition for cooling instabilities develop is that the rate of radiative cooling exceed the external heating rate at the stagnation radius.

@@

Quantitatively, $\rs\propto v_w^{-2}$, implying that $\Mdot\sim v_w^{-3.8 (-2.4)}$ for core (cusp) galaxies.  However, $\Mdot$ may increase even more rapidly as $v_w$ decreases for two reasons: (1) when $v_w$ is comparable or less than the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar bulge and cannot produce a flow with a positive kinetic energy interior to the break radius of the stellar density profile (Appendix \ref{app:be}); (2) For low $v_w$, gas near the stagnation radius becomes thermally unstable, which based on previous studies (e.g.,\citealt{Ciotti+10}) is found to result in time-dependent cycles of alternating high and low accretion states ($\S\ref{sec:cycle}$).

\item The nuclei of galaxies with low mass black holes $\Mbh \lesssim 10^8
  \Msun$ and star formation histories which match their average value derived from cosmological simulations, receive a stellar wind heating rate $v_w\sim 800$ km s$^{-1}$ which is relatively independent of SMBH mass (Fig.~\ref{fig:vwSources}).  The resulting Eddington ratio is predicted to increase weakly with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in moderate tension with the (also weak) downsizing trend of measured nuclear X-ray luminosities of early-type galaxies (e.g., \citealt{Miller+15}).

For thermally stable accretion models, scatter in nuclear X-ray luminosities at fixed $\Mbh$ of the observed 2-4 orders of magnitude can result from a combination of (1) intrinsic scatter in the SMBH scaling relations; (2) stochastic variation in star formation history from galaxy to galaxy, or from time to time due to burstiness in the star formation history (e.g.~\ref{fig:NickPlot2}); (3) Variations in the amount of inflowing mass which is lost to small scale outflows from the SMBH accretion disk, due to variations in the angular momentum of the accreting gas.

\item Only for relatively high X-ray radiative efficiencies similar to the maximum values predicted by ADAF models are the inferred accretion rates of quiescent early-type galaxies below the maximum value consistent with thermally-stable accretion (Fig.~\ref{fig:miller}).  High mass SMBHs are particularly susceptible to thermal instability, given the large stagnation radii that can result from the deep potentials and large break radii of these (mainly core) galaxies.  If the current X-ray sample is instead comprised mainly of thermally unstable nuclei, then a separate branch of low $L_x$ "thermally stable" nuclei may exist, especially at low $M_{\bullet}$.  Such a dichotomy calls into question the accuracy of extrapolating the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ in constraining the SMBH occupation fraction in low mass galaxies (\citealt{Miller+15}).

  \item Low mass black holes grow in the low redshift universe over timescales comparable to the Hubble time (\citet{Heckman+04}).  This requires accretion rates which are too high to be consistent with the maximum allowed for steady-state, thermally stable accretion (Fig.~\ref{fig:bh_growth}).  Low-$M_{\bullet}$ growth and AGN activity must instead be driven by gas supplies external to the nuclear region.

@@

    Overall we conclude that for values of $\Mbh\lsim 10^{8} \Msun$,
    the observed nuclear x-ray luminosities in quiescent, early type
    galaxies could be understood as coming from thermally stable
    steady-state accretion of stellar winds shed in the galactic
    nucleus.  However, we would like to draw attention to the
    following limitations of our model

    \begin{enumerate}
    \item Overall the accretion rate onto the central SMBH will be strongly
    tied to the properties of the stellar population (e.g. age) within
    the sphere of influence of the black hole. Thus, our model cannot
    say anything definitive about the mode accretion for individual
    galaxies which may have significant variations about our assumed
    average star formation histories.
    \item Also, the star formation history of bulges may (and probably
      does) systematically differ from the average star formation
      history for galaxies as a whole.
    \item Furthermore, there could be a radial gradient in the star
      formation history within a given bulge... 
     {\bf AG this section needs to be finished...}
    \end{enumerate}

\section*{Acknowledgments}
We acknowledge helpful conversations with Jerry Ostriker, Eliot
Quataert, .... This work relied on Columbia University's Yeti compute
cluster,and we acknowledge the Columbia HPC support staff for
assistance.  BDM gratefully acknowledges support from NASA {\it Fermi}
grant NNX14AQ68G, NSF grant AST-1410950, and the Alfred P. Sloan
Foundation.

>>>>

In Appendix \ref{app:windheat} we calculate the wind heating rate from
stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter,
$\eta$ (eq.~[\ref{eq:q}]), as a function of age, $\tau_{\star}$, of a
stellar population which is formed impulsively (Fig.~\ref{fig:vwImp}).  
At the earliest times ($\tau_{\star} \lesssim 10^{7}$ yr), the wind
heating rate exceeds 1000 km s$^{-1}$, while much later ($\tau_{\star}
\sim t_{\rm h}$) stellar wind heating dominated by main sequence winds
is much lower, $v^{\star}_{\rm w} \sim 50-100 $ km s$^{-1}$.  As shown below in $\S\ref{sec:combined}$ that for the case of quasi-continuous star
formation representative of the average star formation history (SFH) of loss
mass galaxies, the stellar wind heating rate produced by stellar winds
can also be significant, $v_{\rm w}^{\star} \sim 1000$ km s$^{-1}$.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
  to the total heating rate of the CNM, $\vwO$ ({\it black}),
  including stellar wind heating ({\it orange}), Ia supernovae ({\it
    green}), millisecond pulsars ({\it blue}), and compton heating
  ({\it pink}).  Each heating source varies with black hole mass
  $\Mbh$ calculated for average star formation histories from
  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for
  details).  {\it Middle Panel:} The ratio of the total heating rate
  ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the
  radiating cooling rate ($|\dot{q}_{\rm rad}|$) at the stagnation
  radius. {\it Bottom panel} Parameter $\eta$ characterizing stellar
  mass loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
  $\Mbh$, calculated for average star SFHs from \citealt{MosterNaab+:2013a} and the
  ratio of Ia radius to stagnation radius as a function of $\Mbh$.}
  %The Ia radius calculated from equation~\eqref{eq:rIa} based on
  %convolving the average star formation histories with the SN Ia DTD.
  %The stagnation radius is calculated from \eqref{eq:stag_simple}
  %using the total heating rate for each $\Mbh$ shown in the top panel
  %assuming a cusp galaxy ($\Gamma=0.8$).}
\end{figure}

@@

If the nuclei of elliptical galaxies are heated as expected for the average star formation history of galaxies with
similar mass, then to first order we predict that $\langle
L_{X}/L_{\rm edd}\rangle$ should be a weakly increasing function of BH mass.
This result is in tension with the observed down-sizing trend that the average Eddington ratio is seen to
decrease (albeit weakly) with $M_{\bullet}$, especially in the $\epsilon_X= (\epsilon_{\rm
  bol}/0.1)(\Mdot/\MdotEdd)$ model.  However, one must keep in mind the enormous uncertainty in calculating the luminosity of the accretion flow close to the black hole in a single waveband based on the feeding rate on larger scales.  If disk outflows carry away most of the infalling mass before it reaches X-ray producing radii (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}), then the angular momentum of the infalling gas might also influence the X-ray luminosity, in a way that could depend systematically on the stellar population and hence $M_{\bullet}$.

@@

Figure \ref{fig:bh_growth} (top panel) also shows that $\dot{M}_{\rm
  C} > \dot{M}_{\rm TI}$ across all black hole masses.  This indicates that even if
Compton heating could act to stabilize the flow in a quasi-steady state (which, as already discussed, is unlikely), the magnitude of the heating is insufficient to produce a thermally stable accretion rate given conditions
corresponding to the average star formation history.

@@

\subsection{SMBH Growth Times }
\label{sec:growth}

@@

The bottom panel of Figure~\ref{fig:bh_growth} shows the SMBH growth
time, $t_{\rm grow} \equiv M_{\bullet}/\dot{M}$, for each accretion rate
shown in the top panel.  For SMBHs which accrete steadily at the rate set by the
stellar wind heating due to the average star formation
history of their host galaxies, we see that $t_{\rm grow}$ exceeds the
Hubble time by 1$-$3 orders of magnitude across all $M_{\bullet}$.
Steady accretion therefore cannot explain the growth of low mass black
holes, a fact which is not surprising given that approximately half of
this growth occurs in AGN radiating within 10 per cent of their
Eddington rate (\citealt{Heckman+04}).  Such high accretion rates
likely instead require an source of gas external to the nuclear
region, triggered either by galaxy mergers associated with the
hierarchical growth of structure or thermal instabilities on larger,
galactic scales (e.g.~\citealt{Ciotti+10}, \citealt{Voit+15}).  In support of this,
\citet{Kauffmann&Heckman09} find that the growth of low mass black
holes is dominated by young stellar bulges which have a log normal
distribution of Eddington ratios peaked at $\Mdot/\dot{M}_{\rm edd} \sim
0.01$. That this distribution is insensitive to galaxy properties
suggests that it is set by SMBH feedback instead of the nuclear gas
supply.

@@

\citet{BergerZauderer+:2012a} infer a flattening of the gas density
profile of the host of J1644+57 on radial scales $r \gtrsim 0.4$ pc (their Fig.~6) which looks
qualitatively similar to the shape density profile we predict for core
galaxies (Fig.~\ref{fig:profiles}, solid line).  To obtain such a flattening on the inferred radial scales would require a black hole of $\Mbh\sim 10^7 \Msun$.  However,  this is inconsistent with the break in the gas density seen at $\sim 0.6$ pc by \citet{BergerZauderer+:2012a}, which should correspond to the break radius of the {\it stellar density} profile, thus implying an unrealistically small SMBH mass of $\Mbh\simeq 100\Msun$ according to the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}.

Alternatively, the observed density break in J1644+57 could result from the outer edge of a sub-parsec nuclear star cluster (e.g., \citealt{Carson+15}).  The high stellar densities of such a compact star cluster could greatly enhance the TDE rate (e.g.~\citealt{Stone&Metzger15}), possibly making this association uncoincidental.

@@

We have calculated steady-state models for the hot gaseous circumnuclear media of quiescent galaxies, under the assumption that gas is supplied exclusively by stellar wind mass loss and heated by shocked stellar winds, supernovae and black hole feedback.  We compute solutions for a range of different black hole masses, heating rates, and observationally-motivated stellar density profiles.  Our numerical results (Table \ref{table:models}) are used to verify and calibrate analytic relationships (Appendix \ref{app:rs}, \ref{app:be}).  The latter are in turn used to explore systematically how the SMBH accretion rate varies with black hole mass and the galaxy's star formation history.  Our results for $\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray luminosities of quiescent SMBHs and low luminosity AGN.  They are also used to address key questions such as the thermal stability of the accretion flow.  Our conclusions are summarized as follows.

  \begin{enumerate}
  \item A stagnation radius, $\rs$, divides the nuclear gas between an accretion flow and an
    outward wind. In steady-state the gas inflow rate towards the black hole is proportional to the
    stellar mass enclosed inside of $\rs$.  In the limit of strong heating, the stagnation radius resides interior to the SMBH influence radius and coincides with the Bondi radius (eq.~[\ref{eq:rbondi}]), and the Bernoulli parameter of the flow at large radii is positive (Appendix \ref{app:be}).  In the limit of weak heating ($\zeta < \zeta_c$; eq.~[\ref{eq:zetacrit}]), the stagnation radius moves to large radii, near or exceeding the stellar break radius $r_b \gg r_{\rm inf}$, greatly increasing the density of gas on smaller radial scales.

\item Including the effects of energy transport by electron conduction results in only moderate changes to the key properties of the flow (e.g. stagnation radius, mass accretion rate, and thermal stability) for causal values of the conduction saturation parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).

\item Radiative cooling has a more pronounced influence on the structure of the gas flow.  The approximate condition for cooling instabilities develop at all radii is that the radiative cooling rate exceed the external gas heating rate near the stagnation radius.  This condition is equivalent to the more commonly invoked $t_{\rm cool} \gg t_{\rm ff}$ criterion (e.g.~\citealt{McCourt+12}; \citealt{Li&Bryan14a}).

@@

Quantitatively, $\rs\propto v_w^{-2}$, implying that $\Mdot\propto  v_w^{-3.8 (-2.4)}$ for core (cusp) galaxies.  However, $\Mdot$ can increase even more rapidly with decreasing $v_w$ for two reasons: (1) when $v_w$ is comparable or less than the stellar velocity dispersion ($\zeta < \zeta_c$; eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar bulge and cannot produce a flow with a positive kinetic energy interior to the break radius of the stellar density profile (Appendix \ref{app:be}); (2) For low $v_w$, gas near the stagnation radius becomes thermally unstable, which based on previous numerical studies (e.g.,\citealt{Ciotti+10}) is found to result in time-dependent cycles of alternating high and low accretion states ($\S\ref{sec:cycle}$).

\item Galactic nuclei harboring low mass black holes $\Mbh \lesssim 10^8\Msun$ experiencing star formation histories to match their average derived from cosmological simulations receive stellar wind heating of $v_w\sim 800$ km s$^{-1}$ (Fig.~\ref{fig:vwSources}) sufficient to result in thermally-stable, steady-state accretion.  The resulting average Eddington-normalized accretion rate is predicted to increase weakly with $M_{\bullet}$ (Fig.~\ref{fig:miller}), in tension with the (also weak) downsizing trend of measured nuclear X-ray luminosities of early-type galaxies (e.g., \citealt{Miller+15}).  However, given the large uncertainties in translating predictions for the gas inflow rate on parsec scales to the disk X-ray luminosity, these differences may not be significant.

Thermally stable accretion models can reproduce scatter in nuclear X-ray luminosities at fixed $\Mbh$ of the observed 2-4 orders of magnitude from a combination of (1) intrinsic scatter in the SMBH scaling relations; (2) stochastic variation in star formation history from galaxy to galaxy, or from time to time due to burstiness in the star formation history (e.g.~\ref{fig:NickPlot2}); (3) Variations in the amount of inflowing mass which is lost to small scale outflows from the SMBH accretion disk, due to variations in the angular momentum of the accreting gas.

\item Only for relatively high X-ray radiative efficiencies similar to the maximum values predicted by ADAF models are the inferred accretion rates of quiescent early-type galaxies below the maximum value allowed for thermally-stable accretion (Fig.~\ref{fig:miller}).  Massive galaxies are also particularly susceptible to thermal instability, given the large stagnation radii that can result from the deep potentials and large break radii of these (mainly core) galaxies.  It is thus possible that the current X-ray detected sample is instead comprised mainly of nuclei undergoing non-steady accretion as a part of local thermal instabilities.  In this case a separate branch of low $L_x$ (undetected) thermally-stable nuclei may exist, especially at low $M_{\bullet}$.  Such a dichotomy challenges the practice of extrapolating the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$ to constrain the SMBH occupation fraction in low mass galaxies (\citealt{Miller+15}).

  \item Low mass black holes grow in the low redshift universe over timescales comparable to the Hubble time (\citet{Heckman+04}).  This accretion rates so required are too high to be consistent with the maximum allowed for steady-state, thermally stable accretion (Fig.~\ref{fig:bh_growth}).  Low-$M_{\bullet}$ growth and AGN activity must instead be driven by gas supplied externally to the nuclear region, e.g. due to galaxy mergers or thermal instabilities on larger, galactic scales (e.g.~\citealt{Voit+15}).

@@

%    Overall we conclude that for values of $\Mbh\lsim 10^{8} \Msun$,
 %   the observed nuclear x-ray luminosities in quiescent, early type
  %  galaxies could be understood as coming from thermally stable
   % steady-state accretion of stellar winds shed in the galactic
    %nucleus.

We conclude by drawing attention to the following limitations of our model
    \begin{enumerate}
    \item Overall the accretion rate onto the central SMBH will be strongly
    tied to the properties of the stellar population (e.g. age) within
    the sphere of influence of the black hole. Thus, our model cannot
    say anything definitive about the mode accretion for individual
    galaxies which may have significant variations about our assumed
    average star formation histories.
    \item Also, the star formation history of bulges may (and probably
      does) systematically differ from the average star formation
      history for galaxies as a whole.
    \item Furthermore, there could be a radial gradient in the star
      formation history within a given bulge... 
     {\bf AG this section needs to be finished...}
    \end{enumerate}

\section*{Acknowledgments}
We acknowledge helpful conversations with Greg Bryan, Jules Halpern, Kathryn Johnston, Jerry Ostriker, and Eliot
Quataert.  This work relied on Columbia University's Yeti compute
cluster,and we acknowledge the Columbia HPC support staff for
assistance.  BDM gratefully acknowledges support from NASA {\it Fermi}
grant NNX14AQ68G, NSF grant AST-1410950, and the Alfred P. Sloan
Foundation.
